Just Add IFC! A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/extensions.tex
minor
hmm.
wip

\subsection{IFC-aware language features}
\label{sec:extensions:labeled}

\subsubsection{Labeled objects}

\paragraph{Labeled values}
\paragraph{Labeled references}
\paragraph{Labeled synchronization primitives}

@@

\subsubsection{External effects}
\label{sec:extensions:external}
Our embedding assumes that the target language not have any
primitives that can external-world effects.
%
Indeed, as discussed in Section~\ref{sec:real}, part of the challenge
when considering real languages is precisely imposing this restriction
on the concrete implementation.
%
Yet, external effects are crucial when implementing more complex
real-world applications.
%
For example, code in our modified IFC browser must load resources or
perform XHR to be useful.

>>>>

\subsection{IFC language features}
\label{sec:extensions:labeled}

\paragraph{Labeled values}
%{
%format unlabel = "\mathbf{unlabel}"
%format label = "\mathbf{label}"
%format labelOf = "\mathbf{labelOf}"
In traditional language-based dynamic IFC systems, a label is
associated with values.
%
Hence, a program that, for example, simply writes labeled messages to
a labeled log can operate on both public and sensitive values.
%
In its simplest form, our coarse grained system requires that the
current label of a task be at least at the level of the sensitive data
to reflect the fact that such data is in scope.

Thus, an extension that allows supports such fine-grained explicitly
labeled values is essential.
%
While both LIO and Breeze have such values built-in, our IFC calculus
can be used to encode the labeled values in terms of the |toLabeled|
construct presented in Section~\ref{sec:retrofit}.
%
However, to allow for the inspection of the label of such values (as
in LIO and Breeze) we assume, for simplicity, that the target
language, e.g., the ML-like language from Figure~\ref{fig:ml},
contains pairs: |te  ::= cdots inlinesep (te, te) inlinesep proji te|.
%
Directly, we can define constructs for labeling a value (|label|),
inspecting the label of such values (|labelOf|), and inspecting the
protected value (|unlabel|):
\begin{code}
label il te  @= let x = te in (il, toLabeled il x)
labelOf te   @= proj1 te
unlabel te   @= (proj2 te) (TI unit)
\end{code}
Here, the first projection of the pair contains the label, which is
effectively public (to the task), while the second contains the
``wrapped'' value.
%
Note that |label| first reduces to a values and then wraps it by
sending it to task whose sole role is to protect the value with its
current label (|il|).
%
The latter task protects the value with the supplied label by ensuring
that any task that wishes to inspect the ```labeled value'' must 
raise their current label before calling |unlabel|.
% 
We remark that this simply gives an encoding for labeled values; 
a concrete implementation would likely rely on constructs that are
cheaper than tasks, e.g., abstract data types.
%}

\paragraph{Labeled references}
\paragraph{Labeled synchronization primitives}

@@

\subsection{External effects}
\label{sec:extensions:external}
Our embedding assumes that the target language not have any
primitives that can external-world effects.
%
Indeed, as discussed in Section~\ref{sec:real}, part of the challenge
when considering real languages is precisely imposing this restriction
on the concrete implementation.
%
Yet, external effects are crucial when implementing more complex
real-world applications.
%
For example, code in our modified IFC browser must load resources or
perform XHR to be useful.
